Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-03-05 manuscript/supplements_rsfmri.Rmd
changes of VW and EM added by FB

```{r calc rew two tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor +  (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tp=anova(R1,R0)
```

@@

test_vif=lm(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex + logmFD, data=final_FC)
vif_res=vif(test_vif)
```

@@

```{r calc rew two tp adjusted 3, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + BMI.bl + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +BMI.bl + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tpadj=anova(R1,R0)
```

@@

@@

```{r calc rew three tp adjusted 3, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + BMI.bl + (1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +BMI.bl + (1|subj.ID), data=final_FC)
anvRew2tpadj=anova(R1,R0)
```

@@

```{r calc DMN two tp adjusted 3, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + BMI.bl + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +BMI.bl + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvDMN2tpadj=anova(R1,R0)
```

@@

#### Three timepoints, adjusted for age, sex, average of mFD and baseline BMI (Model CA3)
```{r calc DMN three tp adjusted 3, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + BMI.bl + (1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +BMI.bl + (1|subj.ID), data=final_FC)
anvDMN3tpadj=anova(R1,R0)
```

>>>>

```{r calc rew two tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor +  (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tp=anova(R1,R0)
anvRew2tp
```

@@

test_vif=lm(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex + mean.logmFD, data=final_FC)
vif_res=vif(test_vif)
```

@@

```{r calc rew two tp adjusted 3, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + BMI_BLi + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +BMI_BLi + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tpadj=anova(R1,R0)
```

@@

test_vif=lm(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +  BMI_BLi, data=final_FC)
vif_res=vif(test_vif)
```

@@

```{r calc rew three tp adjusted 3, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + BMI_BLi + (1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +BMI_BLi + (1|subj.ID), data=final_FC)
anvRew3tpadj=anova(R1,R0)
```

@@

```{r calc DMN two tp adjusted 3, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + BMI_BLi + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +BMI_BLi + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvDMN2tpadj=anova(R1,R0)
```

@@

#### Three timepoints, adjusted for age, sex, average of mFD and baseline BMI (Model CA3)
```{r calc DMN three tp adjusted 3, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + BMI_BLi + (1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +BMI_BLi + (1|subj.ID), data=final_FC)
anvDMN3tpadj=anova(R1,R0)
```
